Crop adaptation through gene flow

### 2016-07-10 Crop_adaptation_gene_flow_gj_outline_shortened.tex
Update Crop_adaptation_gene_flow_gj_outline_shortened.tex

Supplement Li's work with the following ideas:

@@

Gene flow between \emph{mexicana} and maize is low enough that only fitness-neutral or advantageous alleles are likely to be passed \cite{slatkin1987gene}.

From \cite{baltazar2005pollination}
Gene flow is probably greater from teosinte to maize.
Certain morphological and flower timing characterists promote genetic isolation between maize and teosinte and slow rates of introgression.
Gene flow from maize to teosinte occurs most easily when teosinte pollinates maize
[[what paper can i cite to mention the gene tb1 and its role in hybridization, viz a viz restricting directionality of teosinte pollen into maize

From \cite{jiang1999genetic}, {bitocchi2009introgression}
Maize-maize introgression
Research on introgression between highland and lowland maize shows adaptive traits being transferred

\cite{bitocchi2009introgression} has a good review of the history of domestication, introduction to Europe, and further development.
\cite{hammer1987collection}\ cites an example in Italy of one domesticated maize adapting to coastal environment by introgressions from another domesticated maize.

>>>>

@@

\cite{bitocchi2009introgression} has a good review of the history of domestication, introduction to Europe, and further development.
